
    \begin{abstract_online}{Melting in Two-Dimensional Gay-Berne Liquid Crystals}{%
        \underline{ Bharti}, D. Deb}{%
        }{%
        School of Physics and Materials Science, Thapar Institute of Engineering & Technology, Patiala, Punjab, India}
    It is well established that the melting of two dimensional (2D) crystals take place through the  unbinding of defects, namely dislocations and disclinations. However, when the constituent particles  are aspherical in shape then there are other types of defects appear in the system due to the particles’  orientational property, as for aspherical particles, configuration is not only defined by their positions  but also by their orientation in space. Systems made up of these particles, show liquid-crystalline  phases. In this work, we have performed molecular dynamics simulations of such systems where the  interaction between the constituent particles is governed by the Gay-Berne potential such that the  particles themselves are like soft ellipses in 2D. We looked at the equilibrium structure by varying  densities and temperature of the system. We have used Voronoi construction to identify the  distribution of different types of defects in the system and then identified specific temperature and  densities at which the system melts from ordered phases (like smectic, nematic) to disordered liquid  phase.  
    
        \textbf{References} \newline{}[1] Joshua A. Anderson, James Antonaglia, Jaime A. Millan, Michael Engel, and Sharon C. Glotzer, Shape and\newline{}Symmetry Determine Two-Dimensional Melting Transitions of Hard Regular Polygons, Phys. Rev. X 7, 021001,\newline{}2017.\newline{}[2] J. M. Kosterlitz and D. J. Thouless, Ordering, metastability and phase transitions in two-dimensional systems,\newline{}Journal of Physics C: Solid State Physics, 6, 1181, 1973.\newline{}[3] D. R. Nelson and B. I. Halperin, Dislocation-mediated melting in two dimensions, Phys. Rev. B, 19,\newline{}2457–2484, Mar 1979.
    \end{abstract_online}
    