
    \begin{abstract_online}{Nucleation and Growth of a Nanobubble on Rough Surfaces}{%
        \underline{S. Maheshwari}$^{1}$, C. v. Kruijsdijk$^{2}$, S. Sanyal$^{1}$, A. Harvey$^{3}$}{%
        \IStag}{%
        $^1$ Shell Technology Centre Bangalore, Plot no. 7, Bangalore Hardware Park, Devanahalli Industrial Park, Mahadeva-Kodigehalli, Bangalore North, Karnataka - 562149, India\newline{}$^2$ Shell Technology Centre Amsterdam, Grasweg 31, 1031 HW Amsterdam, The Netherlands\newline{}$^3$ Shell Technology Centre Houston, 3333 Highway 6 South Houston, Texas 77082, USA}
    We study the nucleation and growth of a nanobubble on rough surfaces by using molecular dynamics simulations. A nanobubble nucleates and grows by the virtue of a heterogenous surface reaction which results in the production of gas molecules near the surface. We study the role of surface roughness in the nucleation and growth behaviour of a nanobubble. We perform simulations at various reaction rates and surface morphology and quantified the growth dynamics of a nanobubble. Our simulations show that after the onset of nucleation, nanobubble grows rapidly with radius following t1/3 behaviour followed by a diffusive growth regime which is marked by t1/2 growth behaviour. This growth behaviour remains independent of surface roughness and reaction rates over the range considered in this study. We also quantified the oversaturation of gas required for the nucleation of a nanobubble and demonstrated its dependence on the surface morphology. 
    
    \end{abstract_online}
    